Relationship between solar wind, $D_{st}$, and plasmasphere mass density on one-hour time scales

### 2015-07-29 paper.tex
Minor edits to Previous Results section

\documentclass[10pt,twocolumn]{article}
\usepackage{graphicx}
\usepackage{subfigure}
\usepackage{fancyhdr}
\usepackage{amssymb,amsmath}
\usepackage{nicefrac}
\usepackage[usenames,dvipsnames]{color}
\usepackage[colorlinks,citecolor=RedViolet,urlcolor=blue]{hyperref}
\usepackage{doi}
\usepackage{setspace}
\usepackage[paperwidth=8.5in, paperheight=11in,top=1in, bottom=1in, left=1in, right=1in]{geometry}
\usepackage[compact]{titlesec}
\usepackage{abstract}

@@

\twocolumn[
  \begin{@twocolumnfalse}
\maketitle
\hrule
\begin{abstract}
This paper looks at how various magnetosphere conditions behave around the onset of geomagnetic events. It confirms results from previous papers that a sudden drop in $D_{st}$ correlates with a spike in equatorial mass density, while adding a level of depth and specification to the applicability of their results. It compares data at 1-hour averages to data at 1-day averages, and briefly to data at 27-day averages to examine if the trend holds at varying time scales and finds that it does, so long as the data is pre-processed to linearly remove a large time scale $F_{10.7}$ dependence. 
By then looking at an hourly average of parameters from 24 hours before event onset to 48 hours after, short timescale trends can be discerned.

@@

\saythanks
% while adding a level of depth and specification to the applicability of their results. It compares data at 1-hour averages to data at 1-day averages, and briefly to data at 27-day averages to examine if the trend holds at varying time scales and finds that it does, so long as the data is pre-processed to linearly remove a large time scale $F_{10.7}$ dependence.

@@

The parameters $\rho_{eq}$ and $F_{10.7}$ used in this work are from the dataset associated with \cite{Denton}, with data available from 1980-1991; all other parameters are from \cite{Reconstruction} over the time range of 1972-2013, which are on a 1-hour time grid. $\rho_{eq}$ is the inferred mass density based on the 3rd harmonic frequency of magnetic field measurements.  The smallest cadence for $\rho_{eq}$ values is 10 minutes.  To compute an hourly average over the same time range as the solar wind parameters, the median of all values in a given hourly range was used.  Fill values were used for hours when no measurements were available.  In cases where $\rho_{eq}$ was available from multiple Geostationary Operational Environmental Satellites (GOES) satellites at the same time in the \cite{Denton} dataset, the value from GOES 7 was selected to avoid overlapping data points.  An overview of the data is given in Figure~\ref{AllData}.

@@

\subsection{Previous Results}
Figure \ref{DailyAverages} show that the trends observed by \cite{Takahashi2010} for one day averages only seems to hold true for the one-day averaged data. Namely that a drop in median daily $D_{st}$ between 1989 and 1991 coincides with a significant spike in $\rho_{eq}$. The correlation seen between $log(\rho_{eq\_27d})$ and $F_{10.7\_27d}$ isn't quite as good in this data as in \cite{Takahashi2010}, but shows the same trend as seen in Figure \ref{ccplot}.

@@

\begin{figure}[htp!]
\centering
\includegraphics[scale=0.42]{paperfigures/F107MDAllData.eps}
\includegraphics[scale=0.42]{paperfigures/ccplot.eps}
\includegraphics[scale=0.42]{paperfigures/F107vsMD.eps}
\caption{(a) All data of $D_{st}$ and $\rho_{eq}$ (b) Correlation between $log(\rho_{eq\_27d})$ and $F_{10.7\_27d}$. (c) $D_{st}$ against $\rho_{eq}$ at one hour and one-day median values.  }
\label{ccplot}
\end{figure}
\clearpage

@@

\begin{figure}[htp]
\centering
\includegraphics[scale=0.5]{paperfigures/nansbyhour.eps}
\includegraphics[scale=0.5]{paperfigures/nansbyhour_storm.eps}
\caption{(a) Number of NaN points per hour of observation in the total data set (b) Data availability relative to average event hour in events where $D_{st}<-80nT$}
\label{nanperhour}
\end{figure}
\clearpage

>>>>

\documentclass[10pt,twocolumn]{article}
\usepackage{graphicx}
\usepackage{fancyhdr}
\usepackage{amssymb,amsmath}
\usepackage{nicefrac}
\usepackage[usenames,dvipsnames]{color}
\usepackage[colorlinks,citecolor=RedViolet,urlcolor=blue]{hyperref}
\usepackage{doi}
\usepackage{setspace}
\usepackage[paperwidth=8.5in, paperheight=11in,top=1in, bottom=1in, left=1in, right=1in]{geometry}
\usepackage[compact]{titlesec}
\usepackage{abstract}
\usepackage{subcaption}

@@

\twocolumn[
  \begin{@twocolumnfalse}
\maketitle
\hrule
\begin{abstract}
This paper compares various magnetosphere conditions around the onset of geomagnetic events. It confirms results from previous papers that a sudden drop in $D_{st}$ correlates with a spike in equatorial mass density under certain conditions, while adding a level of depth and specification to the applicability of their results. It compares data at 1-hour averages to data at 1-day averages to examine if the trend holds at varying time scales and finds that it does, so long as the data is pre-processed to linearly remove a large time scale $F_{10.7}$ dependence. 
By then looking at an hourly average of parameters from 24 hours before event onset to 48 hours after, short timescale trends can be discerned.

@@

\saythanks

@@

The parameters $\rho_{eq}$ and $F_{10.7}$ used in this work are from the dataset associated with \cite{Denton}, with data available from 1980-1991; all other parameters are from \cite{Reconstruction} over the time range of 1972-2013, which are on a 1-hour time grid. $\rho_{eq}$ is the inferred mass density based on the 3rd harmonic frequency of magnetic field measurements.  The smallest cadence for $\rho_{eq}$ values is 10 minutes.  To compute an hourly average over the same time range as the solar wind parameters, the median of all values in a given hourly range was used.  Fill values were used for hours when no measurements were available.  In cases where $\rho_{eq}$ was available from multiple Geostationary Operational Environmental Satellites (GOES) satellites at the same time in the \cite{Denton} dataset, the value from GOES 7 was selected to avoid overlapping data points.  In the dataset, measurements from GOES 7 had the longest time span of coverage.  An overview of the data is given in Figure~\ref{AllData}.

% How does GOES 7 only effect result.

@@

\subsection{Previous Results}

Figure~\ref{ccplot:a} shows the long-term trends of $log(\rho_{eq})$ and $F_{10.7}$ by computing the median in 27-day windows using all non--fill hourly values.  A scatter plot of these two lines is shown in Figure~\ref{ccplot:b}.  The linear correlation is found to be $0.87$.  In comparison, \cite{Takahashi2010} found a correlation coefficient of $0.94$ using measurements from all satellites in the time interval of 1980 to 1992.

The correlation seen between 27-day averages $log(\rho_{eq\_27d})$ and $F_{10.7\_27d}$ isn't quite as good in this data as in \cite{Takahashi2010}, but shows the same trend as seen in Figure \ref{ccplot}.

Figure \ref{DailyAverages} show that the trends observed by \cite{Takahashi2010} for one day averages only seems to hold true for the one-day averaged data. Namely that a drop in median daily $D_{st}$ between 1989 and 1991 coincides with a significant spike in $\rho_{eq}$.

@@

\begin{figure}[htp!]
\centering
\subcaptionbox{All data of $F_{10.7\_27d}$ and $\rho_{eq\_27d}$ \label{ccplot:a}}
{\includegraphics[scale=0.42]{paperfigures/F107MDAllData.eps}}
\subcaptionbox{ Correlation between $log(\rho_{eq\_27d})$ and $F_{10.7\_27d}$, compare to \cite{Takahashi2010} Fig. 14  \label{ccplot:b}}
{\includegraphics[scale=0.42]{paperfigures/ccplot.eps}}
\subcaptionbox{$D_{st}$ against $\rho_{eq}$ at one hour and one-day median values. \label{ccplot:c}}
{\includegraphics[scale=0.42]{paperfigures/F107vsMD.eps}}
\caption{Correlation and comparisons between $F_{10.7}$ and $\rho_{eq}$}
\label{ccplot}
\end{figure}
\clearpage

@@

\begin{figure}[htp]
\centering
\includegraphics[scale=0.5]{paperfigures/nansbyhour.eps}
\includegraphics[scale=0.5]{paperfigures/nansbyhour_storm.eps}
\caption{(a) Number of NaN points per hour of observation in the total data set (b) $\rho_{eq}$ data availability relative to average event hour in events where $D_{st}<-80nT$}
\label{nanperhour}
\end{figure}
\clearpage
